---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# regexcite

<!-- badges: start -->
<!-- badges: end -->

The goal of **regexcite** is to make regular expressions in R more accessible and enjoyable. It provides lightweight helper functions that wrap around `stringr` to simplify common string operations.

## Installation

You can install the development version of **regexcite** from [GitHub](https://github.com/jennybc/regexcite) with:

``` r
# install.packages("devtools")
devtools::install_github("jennybc/regexcite")
```

## Example

A common task when working with strings is splitting a single string into multiple parts. Base R returns a list, but regexcite gives you the character vector directly.
```{r}
library(regexcite)
## basic example code
x <- "alfa,bravo,charlie,delta"
str_split_one(x, pattern = ",")
```

You can also leverage `stringr` features, like controlling the number of splits or using fixed patterns:
```{r}
str_split_one(x, pattern = ",", n = 2)

y <- "192.168.0.1"
str_split_one(y, pattern = stringr::fixed("."))
```

## Motivation
The `str_split_one()` function simplifies `stringr::str_split()` when you know you're working with a single string. It also includes error handling for longer inputs, making it safer and easier to debug.

## Contributing
Pull requests and suggestions are welcome. For major changes, please open an issue first to discuss what you'd like to change.

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.

## License

MIT © 2025 regexcite authors

